---
title: "Tutorial 1"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Set up working directory

```{r wd, echo = TRUE}
getwd() #check where your current working directory is
setwd("/Volumes/GoogleDrive/My Drive/R_Scripts/") #input correct path
getwd() #verify the directory is correct
```

## Install Packages
```{r dp, echo = TRUE}
library(dplyr)
library(tidyverse)
```

## Import files

```{r file}
#demogs <- read.csv("Braskie_R_Workshop/tutorial_01/orig_files/df1_corticalthickness.csv")
```

## Check File Structure and Duplicates

```{r structure}
demogs.vegf <- demogs.vegf[!duplicated(demogs.vegf$Subject),]
demogs.vegf <-demogs.vegf[!is.na(demogs.vegf$CSF_VEGFA_pg_mL),]
```

## Remove Duplicates
```{r duplicates}
```

##Remove rows (subjects) if they are missing value in one column
```{r rowcheck}
```

## Only Keep complete cases
```{r complete}
```

## Join Files Together
```{r merge}
#Left
demogs.vegf <-join(demogs, vegf.new, by="Subject", type="left")
#Right
demogs.vegf <-join(demogs, vegf.new, by="Subject", type="left")
#Both
demogs.vegf <-join(demogs, vegf.new, by="Subject", type="left")
```

#SUBSET DATA FILES BY BASELINE VISIT
```{r subset}
apoe.bl <-subset(apoe, redcap_event_name=="baseline_arm_1")
```


#rename ID column
```{r rename}
#csf <- csf %>% dplyr::rename(Subject.ID = uds_id)
#apoe <- apoe %>% dplyr::rename(Subject.ID = uds_id)
```

#EXTRACT ONLY RELEVANT COLUMNS & RENAME SUBJECT COLUMN
```{r extract}

stru(hhr)
names(hhr)[1] <- "Subject"

stru(apoe.bl)
apoe.bl <- apoe.bl[, c(1, 5)]
names(apoe.bl)[1] <- "Subject"

stru(moca.bl)
moca.bl <- moca.bl[, c(1, 34)]
names(moca.bl)[1] <- "Subject"
```

#COMBINE L & R HEMISPHERE
```{r bilateral}
adrc$CA1_LR_vol <- (adrc$CA1_L_volume + adrc$CA1_R_volume)/2
```

#RECODE DATA
```{r amyloid}
adrc$ab.pos <- ifelse(adrc$biomk_abeta42<192, 1, 0)
table(adrc$ab.pos)

#aaic.upd <-aaic.upd %>%  mutate(ab.pos = if_else(biomk_abeta42 < "192", 1, 0))

```

## Calculate Date Difference
```{r dates}
lp.mri$lp_date <-as.Date(lp.mri$lp_date, "%m/%d/%y")
lp.mri$Study.Date <-as.Date(lp.mri$Study.Date, "%m/%d/%y")
aic.upd$LP.date<- as.Date("2016-01-01")
aaic.upd$lp_mri_datediff<- difftime(aaic.upd$LP.date ,aaic.upd$MRI.date , units = c("days"))
)
```

## Split Data by Median
```{r split}
adrc$high.wmh <-as.factor(ntile(adrc$WMH_Global_normMean, 2) )
```
